---
title: "World Development Indicators Analysis"
author: "Brian Tekadtuera"
date: 02/25/2025
format: 
  html: default
  pdf: default
editor: visual
bibliography: references.bib
---

```{r, echo=FALSE}
#| warning: false
library(tidyverse)

library(knitr)

# Load Data

df <- read.csv("wdi.csv")

# Select relevant columns

df_selected <- df %>% select(country, gdp_per_capita, inflation_rate, unemployment_rate)
```

```{r}
#| warning: false
summary(df_selected)
```

## GDP Per Capita Distribution

```{r gdp_plot, echo=FALSE}
#| warning: false
library(ggplot2)

ggplot(df_selected, aes(x=gdp_per_capita)) +

geom_histogram(binwidth=1000, fill="blue", alpha=0.7) +

labs(title="Distribution of GDP Per Capita (2022)", x="GDP Per Capita (USD)", y="Count")
```
::: {#fig-gdp-per-capita .figure}
_Figure 1: Distribution of GDP per capita for various countries in 2022._
:::

```{r}

```

## GDP vs Inflation Rate

```{r scatter_plot2, echo=FALSE}
#| warning: false
ggplot(df_selected, aes(x=gdp_per_capita, y=inflation_rate)) +

geom_point(color="red", alpha=0.6) +

labs(title="GDP Per Capita vs. Inflation Rate", x="GDP Per Capita (USD)", y="Inflation Rate (%)")
```
::: {#fig-gdp-inflation .figure}
_Figure 2: Relationship between GDP and Inflation._ [@worldbank2022]
:::

```{r scatter_plot, echo=FALSE}
#| warning: false
ggplot(df_selected, aes(x=gdp_per_capita, y=unemployment_rate)) +

geom_point(color="red", alpha=0.6) +

labs(title="GDP Per Capita vs. Unemployment Rate", x="GDP Per Capita (USD)", y="Unemployment Rate (%)")
```
::: {#fig-gdp-unemployment .figure}
_Figure 3: Relationship between GDP and Unemployment._
:::



| Indicator             | Mean   | Median | Min    | Max    |
|-----------------------|--------|--------|--------|--------|
| GDP Per Capita (USD)  | 20346 | 7588 | 259 | 240862 |
| Inflation Rate (%)    | 12.494  | 7.968  | -6.687  | 171.205  |
| Unemployment Rate (%) | 7.269  | 5.537  | 0.130  | 37.862  |

::: {#stat_table .table}
_Figure 4: Summary Statistics for Selected Variables._
:::


#  Analysis & Conclusions

The histogram in @fig-gdp-per-capita shows that the majority of countries have a GDP per capita of between 0-25000, with many outliers
The scatter plot in @fig-gdp-inflation highlights a negative correlation between GDP per capita and inflation rate rate.
The scatter plot in @fig-gdp-unemployment highlights a negative correlation between GDP per capita and unemployment rate.

