---
title: "World Development Indicators Analysis"
author: "Brian Tekadtuera"
date: 02/25/2025
format: 
    revealjs:
        theme: dracula
        transition: fade
---

# Introduction
- Overview of World Development Indicators (2022)
- Focus on economic and social indicators

# Key Indicators
- **GDP per Capita**
- **Inflation Rate**
- **Unemployment Rate**

# Data Overview

```{r setup, include=FALSE}
library(tidyverse)
library(knitr)

# Load Data
df <- read.csv("wdi.csv")

# Select relevant columns
df_selected <- df %>% select(country, gdp_per_capita, inflation_rate, unemployment_rate)
```

```{r echo=FALSE}
summary(df_selected)
```

# Visualizations
## GDP Per Capita Distribution
```{r, echo=FALSE}
ggplot(df_selected, aes(x=gdp_per_capita)) +
  geom_histogram(binwidth=1000, fill="blue", alpha=0.7) +
  labs(title="Distribution of GDP Per Capita (2022)", x="GDP Per Capita (USD)", y="Count")
```

## GDP vs Inflation Rate
```{r, echo=FALSE}
ggplot(df_selected, aes(x=gdp_per_capita, y=inflation_rate)) +
  geom_point(color="red", alpha=0.6) +
  labs(title="GDP Per Capita vs. Inflation Rate", x="GDP Per Capita (USD)", y="Inflation Rate (%)")
```

## GDP vs Unemployment Rate
```{r, echo=FALSE}
ggplot(df_selected, aes(x=gdp_per_capita, y=unemployment_rate)) +
  geom_point(color="red", alpha=0.6) +
  labs(title="GDP Per Capita vs. Inflation Rate", x="GDP Per Capita (USD)", y="Inflation Rate (%)")
```

# Conclusion
- The histogram in @fig-gdp-per-capita shows that the majority of countries have a GDP per capita of between 0-25000, with many outliers
- The scatter plot in @fig-gdp-inflation highlights a negative correlation between GDP per capita and inflation rate rate.
- The scatter plot in @fig-gdp-unemployment highlights a negative correlation between GDP per capita and unemployment rate.
